Towards atomistic resolution structure of phosphatidylcholine headgroup and glycerol backbone at different ambient conditions\footnote{Publication about results presented in the NMRlipids project}

### 2015-05-15 HGmodelMANUSCRIPT/coverLETTER.tex
Final version of cover letter

Please find attached to this message a manuscript entitled `Towards atomistic resolution structure of phosphatidylcholine 
glycerol backbone and choline headgroup at different ambient conditions' by A. Botan et al., which we would like to submit 
for consideration of publication in \textit{Journal of the American Chemical Society} (JACS). In the manuscript a large amount of
existing experimental Nuclear Magnetic Resonance (NMR) data is reviewed and combined with an exceptionally comprehensive 
collection of molecular dynamics (MD) simulation data in order to understand the atomistic resolution structure 
of biologically abundant phospholipid molecules and their assemblies.

>>>>

Please find attached to this message a manuscript entitled `Towards atomistic resolution structure of phosphatidylcholine 
headgroup and glycerol backbone at different ambient conditions' by A. Botan et al., which we would like to submit 
for consideration of publication in \textit{Journal of the American Chemical Society} (JACS). In the manuscript a large amount of
existing experimental Nuclear Magnetic Resonance (NMR) data is reviewed and combined with an exceptionally comprehensive 
collection of molecular dynamics (MD) simulation data in order to understand the atomistic resolution structure 
of biologically abundant phospholipid molecules and their assemblies.
